Summer 2025 ToDo

### 2025-07-08 Relations/Paper/Definitions.tex
Updates to formalization section. Mainly proof environment.

Our Agda formulation of the above definition makes use of the List type constructor, which we import from the \href{https://agda.github.io/agda-stdlib/v2.1/Agda.Builtin.List.html}{Agda standard library}.

@@

\apcomment{Should expand this section, briefly summarize the definition of lists and the relevant lemmas, or
point to standard the library.}

>>>>

Our Agda formulation of the above definition makes use of the List type constructor, which we import from the Agda Standard Library \cite{AgdaLibraryList}.

@@

### 2025-07-08 Relations/Paper/Formalization.tex
Updates to formalization section. Mainly proof environment.

\apcomment{Rephrase this?  Or rewrite this subsection.}

@@

\apcomment{Should articulate the fact that normalization is defined as well-foundedness of the \emph{converse}
relation, per \cite{Terese}.  Will discuss this separately in WF section, but should remind the reader of this
whenever SN/SM comes up. }

@@

The following is a summary of the differences in definition we have used as mentioned in Section \ref{sec:Definitions}.
\begin{itemize}
    \item $\SN$ : We define this via the notion of accessibility rather than the non-existence of infinite reduction sequences.
     See Section \ref{sec:Well-foundedness} for further discussion.
    \item $\NPe$ : We use the equivalent $\NP$ definition.
    \item $\Inc$ : We use the more general property $\RP$.
\end{itemize}

@@

  \verb|NewmansLemma : R isSN → R isWCR → R isCR|.

  We show in Subsection \ref{subsec:newnewman} a generalization of Newman's Lemma using a condition distilled from $\gRP$.
  The formalizations of the remaining theorems are all found in \texttt{ARS-Theorems.agda}.
\end{proof}

\begin{theorem}(Thm 1.2.2 in [Terese])
\begin{description}
  \item[($i$)] $\gCR \implies \gNPe \implies \gUN$
  \item[($ii$)] $\gWN \land \gUN \implies \gCR$
  \item[($iii$)] $\gCRs \implies \gCR$
\end{description}
\end{theorem}

\begin{proof}
    See, \\
    \verb|CR→NP : R isCR → R isNP₌|\\
    \verb|NP→UN : R isNP₌ → R isUN|\\
    \verb|ii : R isWN × R isUN → R isCR|\\
    \verb||\texttt{UN}$^{\to}$ \verb|∧WN→CR : R |\texttt{isUN}$^{\to}$ \verb| → R isWN → R isCR|\\
    \verb|iii : subcommutative R → R isCR|\\
    in \texttt{Theorems.agda}.
\end{proof}
\begin{proof}[Discussion.]
    In $\mathtt{UN^{→}∧WN→CR}$ a more general proof of ($ii$) is given using $\UNto$.
\end{proof}
\apcomment{Perhaps change the fourth implication to use $\times$ instead of $\to$ ??}

\begin{theorem}(Thm. 1.2.3 in [Terese])
  \begin{enumerate}[(i)]
    \item $\gWN \land \gUN \implies \gBP$
    \item $\gBP \land \gInc \implies \gSN$
    \item $\gWCR \land \gWN \land \gInc \implies \gSN$
    \item $\gCR \iff \gCP$ $($the forward implication only holds if the ARS is countable.$)$
  \end{enumerate}
  % \begin{description}
  %   \item[($i$)] $\gWN \land \gUN \implies \gBP$
  %   \item[($ii$)] $\gBP \land \gInc \implies \gSN$
  %   \item[($iii$)] $\gWCR \land \gWN \land \gInc \implies \gSN$
  %   \item[($iv$)] $\gCR \iff \gCP$ ($\gCR \implies \gCP$ only holds if the ARS is countable.)
  % \end{description}
\end{theorem}
\apcomment{Do the same for 1.2.2, and below!}

\begin{proof}
    See \texttt{Theorems.agda},\\
    \verb|i     : R isWN → R isUN → R isBP|\\
    $\mathtt{i^\to}$\hspace{5mm} \verb|: R isWN → R |\texttt{isUN}$^{\to}$ \verb|→ R isBP|\\
    \verb|iiSeq : R isWN → R isUN → R isRP → isWFseq- (~R R)|\\
    \verb|iii   : R isWN → R isWCR → R isRP- → dec SN → R isSN|\\
    \verb|iv    : R isCP → R isCR|
\end{proof}
\apcomment{Apply similar formatting elsewhere.}
\begin{proof}[Discussion.]\hfill
  \begin{description}
    \item[($i$)] In $\mathtt{i^\to}$ we again provide a slight improvement by using $\gUNto$ rather than $\gUN$.
    \item[($ii$)] This proof is inherently classical. In $\mathtt{iiSeq}$, we show that these properties imply $\isWFseqm$; establishing the implication to $\gSN$ would require additional classical assumptions. The definition and further discussion of $\isWFseqm$ are provided in Section~\ref{sec:Well-foundedness}.
    \item[($iii$)] In $\mathtt{iii}$, we replace $\gInc$ with the more general property $\gRPm$. We also assume that $\gSN$ is decidable, as this allows the construction of a witness for whether an element possesses the property $\SN$, which is essential for our proof.
    \item[($iv$)] We did not formalize $\gCR \to \gCP$ as it requires cardinality assumptions. \qedhere
  \end{description}
\end{proof}

% \begin{remark} \hfill
%     \begin{itemize}
%         \item In $\mathtt{i^\to}$ we again provide a slight improvement by using $\gUNto$ rather than $\gUN$.
%         \item ($ii$) is inherently classical. In $\mathtt{iiSeq}$, we show that these properties imply $\isWFseqm$; establishing the implication to $\gSN$ would require additional classical assumptions. The definition and further discussion of $\isWFseqm$ are provided in Section~\ref{sec:Well-foundedness}.
%         \item In $\mathtt{iii}$, we replace $\gInc$ with the more general property $\gRPm$. We also assume that $\gSN$ is decidable, as this allows the construction of a witness for whether an element possesses the property $\SN$, which is essential for our proof.
%         \item We did not formalize $\gCR \to \gCP$ as it requires cardinality assumptions.
%     \end{itemize}
% \end{remark}

>>>>

@@

@@

The following is a summary of the differences in definition we have used as mentioned in Section \ref{sec:Definitions}.
\begin{itemize}
    \item $\SN$ : We define this via the notion of accessibility rather than the non-existence of infinite reduction sequences. Both definitions articulate normalization as well-foundedness of the converse relation. However, different notions of well-foundedness are used in the two definitions. The differences are highlighted in Sections~\ref{sec:Well-foundedness}.
     See Section \ref{sec:Well-foundedness} for further discussion.
    \item $\NPe$ : We use the equivalent $\NP$ definition.
    \item $\Inc$ : We use the more general property $\RP$.
\end{itemize}

@@

  \verb|NewmansLemma : R isSN → R isWCR → R isCR|.
\end{proof}

  We show in Subsection \ref{subsec:newnewman} a generalization of Newman's Lemma using a condition distilled from $\gRP$.
  The formalizations of the remaining theorems are all found in \texttt{Theorems.agda}.

\begin{theorem}(Thm 1.2.2 in [Terese])
\begin{enumerate}[(i)]
  \item $\gCR \implies \gNPe \implies \gUN$
  \item $\gWN \land \gUN \implies \gCR$
  \item $\gCRs \implies \gCR$
\end{enumerate}
\end{theorem}

\begin{proof}
    See \texttt{module Theorem-1-2-2} in \texttt{Theorems.agda}, \\
    \verb|CR→NP : R isCR → R isNP₌|\\
    \verb|NP→UN : R isNP₌ → R isUN|\\
    \verb|ii : R isWN × R isUN → R isCR|\\
    \verb||\texttt{UN}$^{\to}$ \verb|∧WN→CR : R |\texttt{isUN}$^{\to}$ \verb| → R isWN → R isCR|\\
    \verb|iii : subcommutative R → R isCR|\\
\end{proof}
\begin{proof}[Discussion.]
    In $\mathtt{UN^{→}∧WN→CR}$ a more general proof of ($ii$) is given using $\UNto$.
\end{proof}
\apcomment{Perhaps change the fourth implication to use $\times$ instead of $\to$ ??}

\begin{theorem}(Thm. 1.2.3 in [Terese])
  \begin{enumerate}[(i)]
    \item $\gWN \land \gUN \implies \gBP$
    \item $\gBP \land \gInc \implies \gSN$
    \item $\gWCR \land \gWN \land \gInc \implies \gSN$
    \item $\gCR \iff \gCP$ $($the forward implication only holds if the ARS is countable.$)$
  \end{enumerate}
\end{theorem}

\begin{proof}
    See \texttt{module Theorem-1-2-3} in \texttt{Theorems.agda},\\
    \verb|i     : R isWN → R isUN → R isBP|\\
    $\mathtt{i^\to}$\hspace{5mm} \verb|: R isWN → R |\texttt{isUN}$^{\to}$ \verb|→ R isBP|\\
    \verb|iiSeq : R isWN → R isUN → R isRP → isWFseq- (~R R)|\\
    \verb|iii   : R isWN → R isWCR → R isRP- → dec SN → R isSN|\\
    \verb|iv    : R isCP → R isCR|
\end{proof}
\begin{proof}[Discussion.]\hfill
  \begin{description}
    \item[($i$)] In $\mathtt{i^\to}$ we again provide a slight improvement by using $\gUNto$ rather than $\gUN$.
    \item[($ii$)] This proof is inherently classical. In $\mathtt{iiSeq}$, we show that these properties imply $\isWFseqm$; establishing the implication to $\gSN$ would require additional classical assumptions. The definition and further discussion of $\isWFseqm$ are provided in Section~\ref{sec:Well-foundedness}.
    \item[($iii$)] In $\mathtt{iii}$, we replace $\gInc$ with the more general property $\gRPm$. We also assume that $\gSN$ is decidable, as this allows the construction of a witness for whether an element possesses the property $\SN$, which is essential for our proof.
    \item[($iv$)] We did not formalize $\gCR \to \gCP$ as it requires cardinality assumptions. \qedhere
  \end{description}
\end{proof}
